---
title: "Significance of RMSE on Parameters"
author: "Hugo Day"
date: "26 August 2018"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation briefly illustrates how parameters can control how well fitting a linear model can be.

We hope you'll see this can be a quick way to see how significant a variable's contribution to an output may be.

## Comments on Dataset

- A dataset of the demographic and socioeconomic data for Switerland in 1888 is used
- We're concerned with how Fertility fits to the other parameters
- The R^2, root mean squared estimate, will be used to estimate how much of the data is covered

## Interactive slides

In this slide select some variables. A linear model of it's dependence will be created at the percentage of the data variability covered by that model presented.

```{r, echo=FALSE}
# echo=F hides the code
dataSet<-swiss
```

```{r echo = FALSE}
# inputPanel defines the grey border around the slider
# sliderInput sets up a slide bar and names the output `nreps` so it can be accessed in the plot below
  inputPanel(
  selectInput("parameters", label = "Select Variables",multiple=TRUE,choices = c('Agriculture','Examination','Education','Catholic','Infant.Mortality'), selected = 'Catholic'))
```

```{r echo = FALSE}
  renderText({
    listoffactors <- c(input$parameters)
    outputEq<-reformulate(termlabels = listoffactors, response ="Fertility")
    
    # Build linear model based on input factors
    

    model<-lm(outputEq,data=dataSet)
    
    rmse<- (summary(model)$r.squared)
    rmse<-format(rmse,nsmall=2)
    rmseMod<- (summary(model)$r.squared*100)
    rmseMod<-format(rmseMod,nsmall=2)
    
    string<-paste("The model that the Swiss dataset is being fitted to is ", deparse(outputEq),". ")
    
    
    string<-paste(string,"The model chosen has a RMSE of ", rmse,". ")
    string<-paste(string,"This means about ",rmseMod, "% of the data is represented by this model")
  })
```
## Summary

- This simple model has shown how some variables can be much more significant than others
- The R^2 value from an linear model fit can be a useful judge on how significant to the variance a parameter/group of parameters can be
