---
title: "Significance of RMSE on Parameters"
author: "Hugo Day"
date: "26 August 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation briefly illustrates how parameters can control how well fitting a linear model can be.

We hope you'll see this can be a quick way to see how significant a variable's contribution to an output may be.

## Comments on Dataset

- A dataset of the demographic and socioeconomic data for Switerland in 1888 is used
- We're concerned with how Fertility fits to the other parameters
- The R^2, root mean squared estimate, will be used to estimate how much of the data is covered

## Interactive slides

In this slide a table of RMSEs from different model combinations is shown

```{r, echo=FALSE}
# echo=F hides the code
dataSet<-swiss
library(knitr)
```

```{r echo = FALSE}
formCath<-reformulate(termlabels = "Catholic", response = "Fertility")
formEd<-reformulate(termlabels = "Education", response = "Fertility")
formCathEd<-reformulate(termlabels = c("Catholic","Education"), response = "Fertility")
formAll<-reformulate(termlabels = c("Agriculture",
                    "Examination",
                    "Education",
                    "Catholic"), response = "Fertility")

    modelCatholic<-lm(formCath,data=dataSet)
    modelEducation<-lm(formEd,data=dataSet)
    modelCatholicEducation<-lm(formCathEd,data=dataSet)
    modelAll<-lm(formAll,data=dataSet)
    
    rmseModCatholic<- (summary(modelCatholic)$r.squared*100)
    rmseModCatholic<-format(rmseModCatholic,nsmall=2)
    rmseModEducation<- (summary(modelEducation)$r.squared*100)
    rmseModEducation<-format(rmseModEducation,nsmall=2)
    rmseModCatholicEducation<- (summary(modelCatholicEducation)$r.squared*100)
    rmseModCatholicEducation<-format(rmseModCatholicEducation,nsmall=2)
    rmseModAll<-summary(modelAll)$r.squared*100
    rmseModAll<-format(rmseModAll,nsmall=2)
    
    models<-c(deparse(formCath),deparse(formEd),deparse(formCathEd),deparse(formAll))
    rmses<-c(rmseModCatholic,rmseModEducation,rmseModCatholicEducation,rmseModAll)
    modelTable<-data.frame(models,rmses)
    names(modelTable)<-c("Formula","RMSE %")

    kable(modelTable,caption="Some Swiss Models")    

```

## Summary

- This simple model has shown how some variables can be much more significant than others
- The R^2 value from an linear model fit can be a useful judge on how significant to the variance a parameter/group of parameters can be
- Even models with many variables can not describe whole datasets
